Finite element analysis ofmulti-dimensional and simplifiedmodels for beams and plates

### 2023-11-07 AppendixA.tex
symbols

>>>>

\section*{Appendix: Mathematical Preliminaries}
In this appendix, we provide a brief overview of the mathematical spaces and concepts used throughout the dissertation.

\subsection*{The Space \( L^2 \)}
Consider a measurable space \( X \). The set of square-integrable functions over \( X \) with respect to a measure \( \mu \) is called the \( L^2 \) space, formally defined as
\[ L^2(X, \mu) = \{ f: X \to \mathbb{R} \mid \int_X |f|^2 \, d\mu < \infty \}. \]

The inner product in \( L^2 \) space is defined as
\[ (f,g) = \int_X f(x)g(x) \, d\mu \quad \text{for } f, g \in L^2(X, \mu). \]
The norm in \( L^2 \) is given by \( ||f|| = (f,f)^{1/2} \) for \( f \in L^2(X, \mu) \). For a comprehensive treatment, see \cite{Rud53}.

\textcolor{red}{***********************************************}

\subsection*{Spaces of Continuous Functions}

\textbf{The Space \( C^m(a,b) \)}\\
This space consists of functions that are \( m \)-times continuously differentiable in the open interval \( (a, b) \).

\textbf{The Space \( C^m[a,b] \)}\\
Functions in \( C^m[a,b] \) are \( m \)-times continuously differentiable in \( (a, b) \) and have defined right derivatives at \( a \) and left derivatives at \( b \) up to the \( m \)-th order.

\textbf{The Space \( C_0^m(a,b) \)}\\
The space \( C_0^m(a,b) \) contains functions from \( C^m[a,b] \) that vanish on the intervals \( [a, \alpha] \) and \( [\beta, b] \) for some \( a < \alpha < \beta < b \).

\textbf{The Spaces \( C^\infty(a,b) \) and \( C^\infty[a,b] \)}\\
These spaces contain functions that are infinitely differentiable, either on the open interval \( (a, b) \) or on the closed interval \( [a, b] \), respectively.

\textbf{The Space \( C_0^\infty(a,b) \)}\\
It includes all functions from \( C^\infty(a,b) \) that have compact support within \( (a, b) \).

\subsection*{Weak Derivatives and Sobolev Spaces}
Weak derivatives allow us to handle functions that are not classically differentiable. These derivatives are defined in a weak sense through the use of test functions.

\textbf{Definition: First Order Weak Derivative}\\
A function \( v \) is the first order weak derivative of \( u \in L^2(a,b) \) if
\[ (u, \phi') = -(v, \phi) \quad \text{for all } \phi \in C^\infty_0(a,b). \]

\textbf{Definition: Higher Order Weak Derivative}\\
Similarly, \( v \) is the \( m \)-th order weak derivative of \( u \) if
\[ (u, \phi^{(m)}) = (-1)^m(v, \phi) \quad \text{for all } \phi \in C^\infty_0(a,b). \]

\textbf{Sobolev Spaces \( W^m(a,b) \)}\\
The Sobolev space \( W^m(a,b) \) includes functions in \( L^2(a,b) \) with weak derivatives up to order \( m \). The inner product and norm in \( W^m(a,b) \) are defined as
\[ (u,v)_m = (u,v) + (Du, Dv) + \dots + (D^m u, D^m v), \]
\[ ||u||_m = \sqrt{(u,u)_m}. \]

\textbf{Sobolev Spaces \( H^m(a,b) \)}\\
The space \( H^m(a,b) \) is defined as the closure of \( C^m[a,b] \) in \( W^m(a,b) \) with respect to the Sobolev norm \( ||\cdot||_m \).

\subsection*{Main Results}
\textbf{Uniqueness of Weak Derivatives}\\
\begin{thmAH1}
	The \( m \)-th order weak derivative \( D^{(m)}u \) is uniquely determined by \( u \).
\end{thmAH1}

\textbf{Inclusion of Continuously Differentiable Functions}\\
\begin{thmAH2}
	The space \( C^m(\overline{I}) \) is a subset of \( W^m(I) \). For a function \( u \) in \( C^m(\overline{I}) \), the classical and weak derivatives coincide: \( D^{(m)}u = u^{(m)} \).
\end{thmAH2}

% Include more theorems, lemmas, or corollaries as needed
% ...

### 2023-11-07 AppendixB.tex
symbols

>>>>

\section*{Introduction}
In this appendix, we delve into the concept of Sobolev spaces, which are fundamental in the study of partial differential equations and variational problems. Sobolev spaces generalize the notion of differentiability and integrate the concept of weak derivatives, making them crucial in formulating and solving problems with less smooth solutions.

\section*{One-Dimensional Case}
Consider the closed interval \([0,\ell]\). We define a partition of this interval into \(n\) subintervals \([x_{k-1},x_k]\), where each \(x_k\) for \(k=0,1,\ldots,n\) is referred to as a node.

\subsection*{Piecewise Linear Basis Functions}
Let us denote the linear basis functions by \(\phi_i\), where each \(\phi_i\) is associated with a node \(x_i\).

\subsubsection*{Properties}
\begin{itemize}
	\item The restriction of \(\phi_i\) to any subinterval is a linear polynomial.
	\item \(\phi_i \in C^0[0, \ell]\) and \(\phi_i' \in L^2(0, \ell)\).
	\item \(\phi_i(x_i) = 1\) and \(\phi_i(x_j) = 0\) for \(i \neq j\).
	\item Each \(\phi_i\) is supported on \([x_{i-1}, x_{i+1}]\), being zero outside this subinterval.
\end{itemize}

\subsection*{Hermite Cubic Basis Functions}
The Hermite cubic basis functions ensure continuity of the first derivative across nodes. There are two types of basis functions to cover the function value and the derivative continuity.

\subsubsection*{Type One Properties}
\begin{itemize}
	\item Each \(\phi^{(1)}_i\) is a cubic polynomial on its support.
	\item \(\phi^{(1)}_i \in C^1[0,\ell]\).
	\item \(\phi^{(1)}_i\) and \((\phi^{(1)}_i)'\) are continuous; \((\phi^{(1)}_i)''\) is piecewise continuous.
	\item \(\phi^{(1)}_i(x_i) = 1\) and \((\phi^{(1)}_i)'(x_i) = 0\).
\end{itemize}

\subsubsection*{Type Two Properties}
\begin{itemize}
	\item Similar to Type One but designed to ensure that \((\phi^{(2)}_i)'(x_i) = 1\) and \(\phi^{(2)}_i(x_i) = 0\).
\end{itemize}

\section*{Two-Dimensional Case}
In the two-dimensional setting, consider a rectangular domain \(\Omega\) with sides of lengths \(a\) and \(b\), divided into rectangular elements by a grid with spacings \(\delta x\) and \(\delta y\).

\subsection*{Piecewise Bi-Linear Basis Functions}
In two dimensions, basis functions \(\phi_i\) are associated with grid nodes \((x_i, y_i)\) and are bilinear over each rectangular element.

\subsubsection*{Properties}
\begin{itemize}
	\item Within each element, \(\phi_i\) is a bilinear function of the form \(a + bx + cy + dxy\).
	\item For a fixed \(y\), \(\phi_i(\cdot, y)\) is linear in \(x\) and continuous over \([0, a]\); the analogous property holds for fixed \(x\) and varying \(y\).
	\item At node \((x_i, y_i)\), \(\phi_i\) equals 1 and vanishes at all other nodes.
	\item The support of \(\phi_i\) consists of the elements sharing the node \((x_i, y_i)\).
\end{itemize}

\section*{General Properties of Sobolev Spaces}
\subsection*{Weak Derivatives}
The concept of weak derivatives allows us to extend the idea of differentiability to functions that may not be differentiable in the classical sense. A weak derivative is defined in the distributional sense, by integration by parts, where the test functions come from smooth, compactly supported spaces.

\subsection*{Embedding Theorems}
Embedding theorems, such as the Sobolev Embedding Theorem, provide the conditions under which Sobolev spaces are contained within other function spaces, or can be continuously injected into them. These are crucial in understanding the regularity properties of solutions to PDEs.

\subsection*{Traces}
In Sobolev spaces, the trace operator allows us to make sense of the restriction of a function to the boundary of a domain, even when the function is not necessarily continuous.

\subsection*{Sobolev Inequalities}
These inequalities provide bounds on the norms of functions in Sobolev spaces and are essential tools for the analysis of variational problems and PDEs.

\section*{Conclusion}
Sobolev spaces are instrumental in the mathematical formulation and analysis of a wide variety of problems in science and engineering. This appendix provides a foundational overview for understanding these spaces in both one- and two-dimensional contexts.

\section*{References}
The references section should contain all works cited throughout the appendix and main text. It is crucial to attribute ideas and direct quotations to their original sources.

### 2023-11-07 files/Chapter1/1DModel.tex
symbols

    \subsubsection*{Equations of motion}\label{sssec:1D_Model:EquationOfMotion}
    \begin{align}
        \rho A \partial_t^2 w &=& \partial_x V + Q, \label{eq:1D_Model:EquationOfMotion1}\\
        \rho I\partial_t^2 \phi  &=& V + \partial_x M. \label{eq:1D_Model:EquationOfMotion2}
    \end{align}
    In~\eqref{eq:1D_Model:EquationOfMotion1} and \eqref{eq:1D_Model:EquationOfMotion2} $\rho$ denotes the density, $A$ is the area of a cross section, $I$ is the area moment of inertia, $M$ is the moment, $V$ is the shear force and $Q$ is an external force acting on the beam.

    \subsubsection*{Constitutive equations}\label{sssec:1D_Model:ConstitutiveEquation}
    \begin{eqnarray}
        M &=& EI\partial_x \phi, \label{eq:1D_Model:ConstitutiveEquations1}\\
        V &=& AG\kappa^2(\partial_x w - \phi), \label{eq:1D_Model:ConstitutiveEquations2}
    \end{eqnarray}
    $E$ is Young's modulus, $G$ the shear modulus and $\kappa^2$ the shear correction factor.

@@

    As in [VV06] and [LLV09] we use the dimensionless constants
    \begin{equation*}
        \alpha = \frac{A \ell^2}{I} \,\,\, \text{and} \,\,\, \beta
        =\frac{AG\kappa^2 \ell^2}{EI}.
    \end{equation*}

>>>>

    \subsubsection*{Equations of motion}\label{sssec:1D_Model:EquationOfMotion}
    \begin{align}
        \rho A \partial_t^2 w &=& \partial_x V + Q, \label{eq:1D_Model:EquationOfMotion1}\\
        \rho I\partial_t^2 \phi  &=& V + \partial_x M. \label{eq:1D_Model:EquationOfMotion2}
    \end{align}\label{sym:A}\label{sym:V}\label{sym:Iinertia}\label{sym:M}\label{sym:phiT}
    In~\eqref{eq:1D_Model:EquationOfMotion1} and \eqref{eq:1D_Model:EquationOfMotion2} $\rho$ denotes the density, $A$ is the area of a cross section, $I$ is the area moment of inertia, $M$ is the moment, $V$ is the shear force and $Q$ is an external force acting on the beam.

    \subsubsection*{Constitutive equations}\label{sssec:1D_Model:ConstitutiveEquation}
    \begin{eqnarray}
        M &=& EI\partial_x \phi, \label{eq:1D_Model:ConstitutiveEquations1}\\
        V &=& AG\kappa^2(\partial_x w - \phi), \label{eq:1D_Model:ConstitutiveEquations2}\label{sym:kappa2T}
    \end{eqnarray}
    $E$ is Young's modulus, $G$ the shear modulus and $\kappa^2$ the shear correction factor.

@@

    As in [VV06] and [LLV09] we use the dimensionless constants
    \begin{equation*}
        \alpha = \frac{A \ell^2}{I} \,\,\, \text{and} \,\,\, \beta
        =\frac{AG\kappa^2 \ell^2}{EI}.
    \end{equation*}\label{sym:alphabeta}

### 2023-11-07 files/Chapter1/3DModel.tex
symbols

\subsection{Equations of motion and constitutive equations} \label{ssec:3D_Model:EquationofMotion+ConstitutiveEquation}
Consider a vector valued function $u$ defined on domain $\Omega \subset {R}^3$
where $u$ describes the displacement of $\Omega$ in ${R}^3$.
\subsubsection{Equation of motion}\label{ssec:3D_Model:EquationOfMotion}
\begin{eqnarray}
	\rho\partial_t^2 u & = & \textrm{div}T + Q. \label{eq:3D_Model:EM}
\end{eqnarray}

In \eqref{eq:3D_Model:EM}, $\rho$ is the density of the elastic body, $T$ is
the stress tensor with components $\sigma_{ij}$, $Q$ is an external body force
acting on $\Omega$ and $\textrm{div}T$ is the divergence of the tensor $T$ and
represented by
\begin{eqnarray}
	\textrm{div}  T & = &
	\begin{bmatrix}
		\partial_1 \sigma_{11} + \partial_2 \sigma_{12} + \partial_3 \sigma_{13} \\
		\partial_1 \sigma_{21} + \partial_2 \sigma_{22} + \partial_3 \sigma_{23} \\
		\partial_1 \sigma_{31} + \partial_2 \sigma_{32} + \partial_3 \sigma_{33}
	\end{bmatrix}. \label{eq:3D_Model:divT}
\end{eqnarray}

Only small vibrations are considered. This means that the local displacements
and rotations are small. Hence the stress tensor $T$ is symmetric. Let
$\textrm{Tr}(T)$ denote the trace of the stress tensor $T$, that is
\begin{eqnarray}
	\textrm{Tr}(T) & = & \phi_{11} + \phi_{12} + \phi_{13}. \label{eq:stress_tensor_t}
\end{eqnarray}

@@

\subsubsection*{Strain}\label{sssec:3D_Model:Strain}
Infinitesimal strain tensor is defined on $\Omega$ as $\mathcal{E}$, with components
\begin{eqnarray}
	\varepsilon_{ij} = \frac{1}{2}\left( \frac{\partial u_i}{\partial x_j} + \frac{\partial u_j}{\partial x_i} \right). \label{eq:3D_Model:Strain}
\end{eqnarray}

@@

\subsubsection*{Hooke's law in terms of $E$ and $\nu$}\label{sssec:3D_Model:Hooke'sLaw1}
\begin{eqnarray}
	\mathcal{E} = \left( \frac{1+\nu}{E} \right)T - \frac{\nu}{E}\textrm{Tr}(T)I,  \label{eq:3D_Model:HL}
\end{eqnarray} where $E$ is Young's Modulus and $\nu$ is Poisson's ratio.

@@

Set \[\tau = \frac{t}{t_0},\quad \xi_i = \frac{x_i}{\ell},\quad {u}^*(\xi,\tau) = \frac{1}{\ell}{u}(x,t), \quad Q^{*} = \ell G \kappa^2 Q, \]
\[ \text{and} \ \,\,\, \sigma_{ij}^*(\xi,\tau) = \frac{1}{G\kappa^2}\sigma_{ij}(x,t),\]

@@

The dimensionless form of \eqref{eq:3D_Model:HL} and \eqref{eq:3D_Model:CE} are
\begin{eqnarray*}
	\mathcal{E} = \frac{G \kappa^2}{E} \left[ (1+\nu)T^* - \nu \textrm{Tr}(T^*)I \right]
\end{eqnarray*}

@@

Introduce a dimensionless constant
\begin{eqnarray*}
	\gamma= \frac{G\kappa^2}{E}.
\end{eqnarray*} Using this dimensionless constant,
\begin{eqnarray}
	\mathcal{E} = \gamma(1+\nu)T^* - \gamma\nu \textrm{Tr}(T^*)I \label{DM_H_E}
\end{eqnarray}
and
\begin{eqnarray}
	T^* = \frac{1}{\gamma(1+\nu)}\mathcal{E} + \frac{\nu}{\gamma(1+\nu)(1-2\nu)}\textrm{Tr}(\mathcal{E})I. \label{DM_H_T}
\end{eqnarray}

@@

\subsection{Model problems}\label{ssec:3D_Model:ModelProblems}
Suppose $\Omega \subset R_3$ is the reference configuration for a solid
executing small vibrations. The boundary of $\Omega$ can be divided into two
distinct parts, referred to as $\Sigma$ and $\Gamma$. The following will be
considered a model problem for a three-dimensional elastic body.
\begin{enumerate}
	\item[] The equations of motion \eqref{eq:3D_Model:EM-D} and \eqref{eq:3D_Model:divT-D} is satisfied in $\Omega$;
	\item[] Hooke's law \eqref{eq:3D_Model:CE-D} is satisfied in $\Omega$;
	\item[] The displacement $u = u_\Sigma$ is specified on
		$\Sigma$;
	\item[] The traction $Tn = t_\Gamma$ is specified on
		$\Gamma$.
\end{enumerate}

@@

\subsection{Variational form}\label{ssec:3D_Model:VariationalForm}
Let $\phi \in C({\Omega})$ be an arbitrary vector valued function. Multiplying
$\phi$ to equation \eqref{eq:3D_Model:EM-D} and integrating over the domain
$\Omega$ results in,

@@

The divergence formula gives
\begin{eqnarray*}
	\int_{\Omega} \textrm{div}(T)\cdot \phi \ dV & = & -\int_{\Omega} \textrm{Tr}(T\Phi) \ dV + \int_{\partial \Omega} Tn\cdot \phi dS.
\end{eqnarray*}
Therefore,
\begin{align*}
	\int_{\Omega} (\partial_t^2 u)\cdot \phi \ dV = -\int_{\Omega} \textrm{Tr}(T\Phi) \ dV +
	\int_{\Omega} Q\cdot\phi \ dV + \int_{\partial \Omega} Tn\cdot \phi \ dS.
\end{align*}
\\

@@

\subsubsection{Bilinear forms and integral}\label{sssec:3D_Model:BilinearForm}
Define the bilinear forms
\begin{eqnarray}
	b(u,\phi) = \int_\Omega~c_1\textrm{Tr}({\cal E}\Phi)+ c_2\textrm{Tr}({\cal E})
	\textrm{Tr}(\Phi) ~dV \label{eq:3D_Model:Bilinear}
\end{eqnarray}
and
\begin{eqnarray}
	c(u,\phi) = \int_\Omega~ (\partial^2_t u) \cdot \phi~dV \label{eq:3D_Model:Bilinear_c}
\end{eqnarray}
with $\displaystyle c_1 = \frac{1}{\gamma(1+\nu)}$ and $\displaystyle c_2 = \frac{\nu}{\gamma(1+\nu)(1-2\nu)}$.\\

@@

Problem 3D-1
\begin{eqnarray*}
	T(\Omega) & = & \left\{ \phi \in C^1(\bar{\Omega}) \ | \ \phi = 0 \ \textrm{ on } \ \Gamma \right\}
\end{eqnarray*}

@@

\subsubsection{Problem 3D-1V}\label{sssec:3D_Model:Problem3D1V}
Find a function $u$ such that for all $t>0$, $u \in T(\Omega)$ and
\begin{align}
	c(u,\phi) = -b(u,\phi) + (Q,\phi), \label{eq:3D_Model:Problem3D1VEq}
\end{align}
for all $\phi \in T(\Omega)$\\

>>>>

\subsection{Equations of motion and constitutive equations} \label{ssec:3D_Model:EquationofMotion+ConstitutiveEquation}
Consider a vector valued function $u$ defined on domain $\Omega \subset {R}^3$ \label{sym:Omega} \label{sym:Rn}
where $u$\label{sym:u} describes the displacement of $\Omega$ in ${R}^3$.
\subsubsection{Equation of motion}\label{ssec:3D_Model:EquationOfMotion}
\begin{eqnarray}
	\rho\partial_t^2 u & = & \textrm{div}T + Q. \label{eq:3D_Model:EM}
\end{eqnarray} \label{sym:rho} \label{sym:partial_diff} \label{sym:T} \label{sym:Q}

In \eqref{eq:3D_Model:EM}, $\rho$ is the density of the elastic body, $T$ is
the stress tensor with components $\sigma_{ij}$\label{sym:sigmaij}, $Q$ is an external body force
acting on $\Omega$ and $\textrm{div}T$\label{sym:divT} is the divergence of the tensor $T$ and
represented by
\begin{eqnarray}
	\textrm{div}  T & = &
	\begin{bmatrix}
		\partial_1 \sigma_{11} + \partial_2 \sigma_{12} + \partial_3 \sigma_{13} \\
		\partial_1 \sigma_{21} + \partial_2 \sigma_{22} + \partial_3 \sigma_{23} \\
		\partial_1 \sigma_{31} + \partial_2 \sigma_{32} + \partial_3 \sigma_{33}
	\end{bmatrix}. \label{eq:3D_Model:divT}
\end{eqnarray}

Only small vibrations are considered. This means that the local displacements
and rotations are small. Hence the stress tensor $T$ is symmetric. Let
$\textrm{Tr}(T)$\label{sym:TrT} denote the trace of the stress tensor $T$, that is
\begin{eqnarray}
	\textrm{Tr}(T) & = & \sigma_{11} + \sigma_{22} + \sigma_{23}. \label{eq:stress_tensor_t}
\end{eqnarray}

@@

\subsubsection*{Strain}\label{sssec:3D_Model:Strain}
Infinitesimal strain tensor is defined on $\Omega$ as $\mathcal{E}$\label{sym:mathcalE}, with components
\begin{eqnarray}
	\varepsilon_{ij} = \frac{1}{2}\left( \frac{\partial u_i}{\partial x_j} + \frac{\partial u_j}{\partial x_i} \right). \label{eq:3D_Model:Strain}
\end{eqnarray}\label{sym:varepsilonij}

@@

\subsubsection*{Hooke's law in terms of $E$ and $\nu$}\label{sssec:3D_Model:Hooke'sLaw1}\label{sym:E} \label{sym:nu}
\begin{eqnarray}
	\mathcal{E} = \left( \frac{1+\nu}{E} \right)T - \frac{\nu}{E}\textrm{Tr}(T)I,  \label{eq:3D_Model:HL}
\end{eqnarray} where $E$ is Young's Modulus and $\nu$ is Poisson's ratio.

@@

Set \[\tau = \frac{t}{t_0},\quad \xi_i = \frac{x_i}{\ell},\quad {u}^*(\xi,\tau) = \frac{1}{\ell}{u}(x,t), \quad Q^{*} = \ell G \kappa^2 Q, \]
\[ \text{and} \ \,\,\, \sigma_{ij}^*(\xi,\tau) = \frac{1}{G\kappa^2}\sigma_{ij}(x,t),\]\label{sym:t}\label{sym:G}\label{sym:tau}\label{sym:xi}\label{sym:Qstar}\label{sym:sigmaijstar}\label{sym:ell}\label{sym:kappa2}

@@

The dimensionless form of \eqref{eq:3D_Model:HL} and \eqref{eq:3D_Model:CE} are
\begin{eqnarray*}
	\mathcal{E} = \frac{G \kappa^2}{E} \left[ (1+\nu)T^* - \nu \textrm{Tr}(T^*)I \right]
\end{eqnarray*}\label{sym:I}

@@

Introduce a dimensionless constant
\begin{eqnarray*}
	\gamma= \frac{G\kappa^2}{E}.
\end{eqnarray*}\label{sym:gamma}

Using this dimensionless constant,
\begin{eqnarray}
	\mathcal{E} = \gamma(1+\nu)T^* - \gamma\nu \textrm{Tr}(T^*)I \label{DM_H_E}
\end{eqnarray}
and
\begin{eqnarray}
	T^* = \frac{1}{\gamma(1+\nu)}\mathcal{E} + \frac{\nu}{\gamma(1+\nu)(1-2\nu)}\textrm{Tr}(\mathcal{E})I. \label{DM_H_T}
\end{eqnarray}

@@

\subsection{Model problems}\label{ssec:3D_Model:ModelProblems}
Suppose $\Omega \subset R_3$ is the reference configuration for a solid
executing small vibrations. The boundary of $\Omega$ can be divided into two
distinct parts, referred to as $\Sigma$ and $\Gamma$. The following will be
considered a model problem for a three-dimensional elastic body.
\begin{enumerate}
	\item[] The equations of motion \eqref{eq:3D_Model:EM-D} and \eqref{eq:3D_Model:divT-D} is satisfied in $\Omega$;
	\item[] Hooke's law \eqref{eq:3D_Model:CE-D} is satisfied in $\Omega$;
	\item[] The displacement $u = u_\Sigma$ is specified on
		$\Sigma$;
	\item[] The traction $Tn = t_\Gamma$ is specified on
		$\Gamma$.
\end{enumerate} \label{sym:n}\label{sym:SigmaGamma}

@@

\subsection{Variational form}\label{ssec:3D_Model:VariationalForm}
Let $\phi \in C({\Omega})$ be an arbitrary vector valued function. Multiplying
$\phi$ to equation \eqref{eq:3D_Model:EM-D} and integrating over the domain
$\Omega$ results in, \label{sym:Cn} \label{sym:phi}

@@

The divergence formula gives
\begin{eqnarray*}
	\int_{\Omega} \textrm{div}(T)\cdot \phi \ dV & = & -\int_{\Omega} \textrm{Tr}(T\Phi) \ dV + \int_{\partial \Omega} Tn\cdot \phi dS.
\end{eqnarray*}
Therefore,
\begin{align*}
	\int_{\Omega} (\partial_t^2 u)\cdot \phi \ dV = -\int_{\Omega} \textrm{Tr}(T\Phi) \ dV +
	\int_{\Omega} Q\cdot\phi \ dV + \int_{\partial \Omega} Tn\cdot \phi \ dS.
\end{align*}

@@

\subsubsection{Bilinear forms and integral}\label{sssec:3D_Model:BilinearForm}
Define the bilinear forms
\begin{eqnarray}
	b(u,\phi) = \int_\Omega~c_1\textrm{Tr}({\cal E}\Phi)+ c_2\textrm{Tr}({\cal E})
	\textrm{Tr}(\Phi) ~dV \label{eq:3D_Model:Bilinear}
\end{eqnarray}\label{sym:b}
and
\begin{eqnarray}
	c(u,\phi) = \int_\Omega~ (\partial^2_t u) \cdot \phi~dV \label{eq:3D_Model:Bilinear_c}
\end{eqnarray}
with $\displaystyle c_1 = \frac{1}{\gamma(1+\nu)}$ and $\displaystyle c_2 = \frac{\nu}{\gamma(1+\nu)(1-2\nu)}$.\\

@@

Problem 3D-1
\begin{eqnarray*}
	T(\Omega) & = & \left\{ \phi \in C^1(\bar{\Omega}) \ | \ \phi = 0 \ \textrm{ on } \ \Gamma \right\}
\end{eqnarray*}\label{sym:TOmega}

@@

\subsubsection{Problem 3D-1V}\label{sssec:3D_Model:Problem3D1V}
Find a function $u$ such that for all $t>0$, $u \in T(\Omega)$ and
\begin{align}
	c(u,\phi) = -b(u,\phi) + (Q,\phi), \label{eq:3D_Model:Problem3D1VEq}
\end{align}\label{sym:c}
for all $\phi \in T(\Omega)$\\
